Revisiting Multi-Domain Machine Translation

### 2020-04-24 2020/coling2020/multidomain.tex
more work on continuous learning and formatting, we still lack results

For all models, we set the embeddings size and the hidden layers size to~512. Transformers use multi-head attention with 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 cells. The multi-domain residual system (see description below) additionally use an adaptation block in each transformer layer, composed of 2-layer perceptron, with an inner RELU activation function operating on normalized entries of dimension 1024. The gated variant is made of a dense layer, followed by a layer normalization and a sigmoid activation.
% The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.
 %
Training use a batch size of~128; optimization uses Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$ and Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ for all layers.\fyDone{Describe the block adaptation layer - voir slides} 
 % All our systems are implemented in OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein17opennmt}.
\subsection{Multi-domain systems \label{ssec:systems}}
\fyDone{Remove Gated residual}
Our comparison of multi-domain systems includes the following reimplementations of recent proposals from the literature:
\begin{itemize}
\item a system using domain control as in \cite{Kobus17domaincontrol}: domain information is introduced either as an additional token for each source sentence (\system{DC-Tag}), or introduced in the form of a supplementary feature for each word (\system{DC-Feat}).
\item a system using lexicalized domain representations \cite{Pham19generic}: word embeddings are composed of a generic and a domain specific part (\system{LDC-Feat});
\item the three proposals of \cite{Britz17mixing}. \system{TTM} is a feature-based approach where the domain tag is introduced as an extra word \textsl{on the target side}. Training is performed with reference tags and inference is performed with predicted tags, just like for regular target words. \system{DM} is a multi-task learner where a domain classifier is trained on top the MT encoder, so as to make it aware of domain differences; \system{ADM} is the adversarial version of \system{DM}, pushing the encoder towards learning domain-independent source representations. Note that these methods only use domain tags during training.
\item the multi-domain model of \cite{Zeng18multidomain} (\system{WDCMT}): in this approach, two representations, a domain-agnostic and a domain-specialized representation of the input are simultaneously processed; supervised classification models and adversarial training are used to compute these representations.\footnote{For this system, we use the available RNN-based system from the authors (\url{https://github.com/DeepLearnXMU/WDCNMT}\fyDone{URLs}) which does not directly compare to the other, Transformer-based, systems; the improved version of \cite{Su19exploring} seems to produce comparable, albeit slightly, improved results.}\fyTodo{Check this}
\item an original, multi-domain, version of the approach of \newcite{Bapna19simple}, denoted \system{MDL Res}, where a domain-specific adaptation module is included in all the Transformer layers; within each layer, residual connexions make it possible to by-pass this module.
  % In a variant (\system{MDL Gated}), we use a gating mechanism to merge computations using the the adapter modules and with those that don not.
Contrarily to \cite{Bapna19simple}, we do not start with a trained generic system, but learn the multi-domain from scratch.\fyDone{Check this.}
\end{itemize}

@@

\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}|} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c||}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
    \system{Mixed-Bal}   &  35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5 & 40.3  & 51.4 \\ %& \\
    \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.8 & 53.8\\
   \system{FT-Block}     & 37.3 & \SB{57.9} & 53.9 & 33.8 & \SB{46.7} & \SB{90.2}  & 42.3 & 53.3 \\ \hline % & 20.5\\ \hline
 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & \SB{80.5} &41.7 & 50.1    \\%    & 21.8 \\
    \system{DC-Feat}      & 37.7  & 54.9 & 49.5   & 32.9 & 43.6 & \SB{79.9} &41.4 & 49.9   \\% & \SW{21.7} \\
    \system{LDC-Tag}     & 37.0   & 54.7 & 49.9 & 33.9 & 43.6 & \SB{79.9} & & 49.8          \\% & 22.1 \\ 
    \system{TTM}            & 37.3 & 54.9 & 49.5 & 32.9 & 43.6 & \SB{79.9} &41.1 & 49.7     \\% &  23.4 \\
    \system{DM}             & \SW{35.6} & \SW{49.5}  & \SW{45.6}& \SW{29.9} & \SW{37.1} & \SW{62.4} & 39.7 & 43.8 \\ % & 22.6\\
    \system{ADM}           & 36.4 & \SW{53.5}  & \SW{48.3} & \SW{32.0} & \SW{41.5} & \SW{73.4} & 40.7 & 47.5 \\% & 23.3 \\
    \system{WDCMT}       & 34.6 & 51.7 & 47.5 & 29.4 & 36.5 & 49.3 & & 41.5 \\ % & 20.4 \\
    \system{MDL Res}     & 37.9 & \SB{56.0}  & \SB{51.2}   & 33.5   &  44.4  & \SB{88.3} & 42.1 & 51.9 \\%  & \SW{21.2} \\
    \hfill MDL Res (gen)    & 37.7 & 51.0 & 34.0 & 30.4 & 34.2 & 15.2 & 36.4 & 33.7\\
%    \system{MDL Gated} & 37.7 & 56.5 & 53.2 & 34.1 & 44.6 & 90.7 & 42.3 & 53.3&\\
     \hline
  \end{tabular}
  \caption{Translation performance of various MDMT systems. We report the BLEU score for each domain, as well as domain-weighted (w\domain{avg}) and unweighted (\domain{avg}) averages. Boldface denotes significant differences with respect to the \system{Mix-Nat} system. Scores for the \domain{news} domain correspond to the out-of-domain scenario (see Section~\ref{ssec:redomains}).}
  \label{tab:performance}
\end{table*}
\fyTodo{Fill the table with all results, including a comparison with *RNNs* for wcmd}\fyTodo{Do we have significancy tests for averages?}
\fyDone{A new column for the News domain with predicted domains (except for the generic case).}

@@

Table~\ref{tab:redomains} summaries the results of four experiments where we artificially redefine the boundaries of domains, with the aim to challenge requirements [P2-TUN], [P3-HET], and [P4-ERR]. In first three, we randomly \emph{split} one corpus in two parts and proceed as if this corresponded to two actual domains. A MD system should detect that these two pseudo-domains should be mutually beneficial, and should be hardly affected by this change with respect to the baseline scenario (no split). In this situation, we should expect MDMT to even surpass fine-tuning separately on each of these dummy domain, as MDMT exploits all data, where fine-tuning focuses only on a subpart. In testing, we decode the test set twice, once with each pseudo-domain tag. Note that this makes no difference for \system{TMM}, \system{ADM}, \system{ADM} and \system{WDCMT}, which do not use domain tags in testing.
In the \textsl{merge} experiment, we do the reverse and merge two corpora in training, in order to assess the robustness with respect to heterogenous domains. We then translate the two corresponding test sets with the same (merged) system.

@@

We now turn to requirement [P5-UNK], and translate test sentences from a domain unseen in training (\domain{news}). For each test sentence, we automatically predict the most likely domain tag, and use it for decoding. Results are in the rightmost column of Table~\ref{tab:performance}. In this configuration, all systems do worse than the baseline, sometimes by a large margin.\fyTodo{Check significance, To be completed}

\subsubsection{Coping with a growing number of domains}
Another series of experiments evaluate the ability to dynamically handle suplementary domains (requirement [P6-DYN]) as follows. Starting with the existing MD systems of Section~\ref{ssec:rawperformance}, we introduce an extra domain (\domain{News}) and resume training with this new mixture of data\footnote{The design of a proper balance between domains in training is again of utmost importance for achieving optimal performance: since our goal is to evaluate all systems in the same conditions, we consider a basic mixing policy based on the new training distribution. This is of course detrimental to the small domains, for which the ``negative transfer'' effect is stronger than for larger domains.} for 50,000 additional iterations.\fyDone{Training regime of continuation} We contrast this approach with retraining all systems from scratch and report differences in performance in Table~\ref{tab:warmrestart}.
We expect that a proper MDMT system should not be significantly affected by the addition of a new domain, and reach about the same performance as if the training included this domain from scratch. Note that from a practical viewpoint, dynamically integrating new domains is straightforward for \system{DC-Tag}, \system{DC-Feat} or \system{TTM} where new domains merely add new labels. It is less simple for \system{LDC-Tag} and \system{MDL~Res}\fyDone{Complete effects of new domain}, for which the number of possible domains is built in the architecture and has to be anticipated from the begining. This makes another difference between domain-bounded MT-systems, for which the number of possible domains is limited and truely open-domain systems.% , which seamlessly integrate additional domains.

\begin{table*}
  \begin{tabular}{|p{3cm}|*{9}{r|}} \hline
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{news}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline

    \system{Mixed-Nat}  & 37.3  & 54.6   & 50.1   & 33.5  & 43.2  & 77.5  & 23.5 & 41.1 & 49.4 \\
    \system{FT-Full}       & 37.7  & 59.2   & 54.5   & 34.0  & 46.8  & 90.8  & **** & 42.8 & 53.8 \\ \hline\hline
     \system{DC-Feat}     & 37.4 & 54.9   & 50.0    & 34.7  &  43.9  & 79.6 & 28.9 \\
                                    & 36.9 & 53.7   & 49.1    & 33.7  &  42.8  & 74.1 & 28.9 &\\
    \system{DC-Tag}      &  37.7 & 54.5   & 49.9    &  34.8 &  43.9  & 78.8 & 29.5 \\
                                   & 38.0  & 54.0   & 48.8    & 33.5  &  42.7  &73.2  & 28.3& \\
    \system{TTM}           &  37.3 & 54.4   & 49.6    & 33.8  &  42.9  &78.1  & 29.1 \\
                                   & 36.8  & 53.4   & 47.9    & 32.4  &  42.5  &72.8  & 28.4& \\
    \system{LDC-Tag}    & 37.0   & 54.6  & 49.6    & 34.3  &  43.0  &77.0  & 28.7 \\
    continual                 &&&&&& \\
    \system{DM}            &36.0 &51.3&46.8&31.8&39.8&65.7&27.0 \\
                                  &36.5&51.6&47.3&31.7&40.3&65.7&25.8& \\
    \system{ADM}          &36.6&54.2&49.1&32.9&42.1&75.7&28.7 \\
                                  &  36.9 &53.5&48.3&32.7&41.7&70.7&26.8& \\
    \system{WDCMT}     &34.8  &51.8&47.8&30.7&37.3&49.3&25.9 \\
    continual                 &&&&&&&& \\
    \system{MDL-Res}    &37.7   & 55.6   & 51.1   & 34.4  & 44.5  & 87.5  & 29.1 & & \\
     continual                & 37.45 & 56.09 & 51.11 & 34.04  &  44.29 & 87.32 & 28.35 & \\
     \hline
  \end{tabular}
  \caption{Ability to handle new a domain: BLEU performance in ``resume training'' mode compared to a complete training session.}
  \label{tab:warmrestart}
\end{table*}
\fyTodo{Fill the table, significancy testing against full learning condition, for each domain}

We can first compare the results of coldstart training with six (Table~\ref{tab:performance}) or seven domains (Table~\label{tab:warmrestart}): the most striking observation is that the extra training data is detrimental for all systems and all domains,\fyTodo{is this significant ?}. Increasing the heterogeneity of the mix hurts performance in all domains, again the sign that the domain are quite well separated. Comparing now the coldstart with the warmstart scenario, we see that the former is always significantly better for \domain{news}, as expected, and that resuming training can negatively impact the performance on other domains - this happens notably for \system{DC-Tag} and \system{TTM}. In this setting, and, XXX\fyTodo{To be completed} and especially \system{MDL Res} show the smaller average loss, with the latter achieving the better balance of total training cost and average translation performance over all systems.

@@

\subsection{Automatic domains \label{ssec:autodomains}}
In this section, we experiment with automatic domains, obtained by clustering sentences into $k=30$ classes using the k-means algorithm based on generic sentence representations obtained via mean pooling as in section~\ref{ssec:corpora}. This allows us to evaluate requirement [P7-scale], training and testing our systems as if these domains were genuine. We also note that many of these classes are mere split of the large \domain{med}, while a few number of classes being mix of two existing domains. We are thus in a position to reiterate in more realistic conditions the measurements of section~\label{ssec:}, and to test whether multi-domain systems can effectively take advantage from the cross-domain similarities, and to eventually perform better that fine-tuning.

Results are in table~\ref{tab:subdomains}.\fyTodo{Fill the tables with automatic and existing domains - we will have significancy results for the existing domains, for the other may be for larger classes we will have enough test instances?}

@@

Multi-domain translation was already proposed for statistical MT (eg.\ \cite{Banerjee10combining,Clark12onesystem,Sennrich13multidomain,Huck15mixeddomain}).\fyTodo{Add also topic models refs} Two main strategies were considered: instance-based, involving a measure of similarities between train and test domains; feature-based, where domain labels give rise to additional features.

>>>>

For all models, we set the embeddings size and the hidden layers size to~512. Transformers use multi-head attention with 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 cells. The multi-domain residual system (see description below) additionally use an adaptation block in each transformer layer, composed of 2-layer perceptron, with an inner RELU activation function operating on normalized entries of dimension 1024. The gated variant is made of a dense layer, followed by a layer normalization and a sigmoid activation.
% The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.
 %
Training use a batch size of~128; optimization uses Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$ and Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ for all layers.\fyDone{Describe the block adaptation layer - voir slides} 
 % All our systems are implemented in OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein17opennmt}.
\subsection{Multi-domain systems \label{ssec:systems}}
\fyDone{Remove Gated residual}
Our comparison of multi-domain systems includes the following reimplementations of recent proposals from the literature:
\begin{itemize}
\item a system using domain control as in \cite{Kobus17domaincontrol}: domain information is introduced either as an additional token for each source sentence (\system{DC-Tag}), or introduced in the form of a supplementary feature for each word (\system{DC-Feat}).
\item a system using lexicalized domain representations \cite{Pham19generic}: word embeddings are composed of a generic and a domain specific part (\system{LDC-Feat});
\item the three proposals of \newcite{Britz17mixing}. \system{TTM} is a feature-based approach where the domain tag is introduced as an extra word \textsl{on the target side}. Training uses reference tags and inference is performed with predicted tags, just like for regular target words. \system{DM} is a multi-task learner where a domain classifier is trained on top the MT encoder, so as to make it aware of domain differences; \system{ADM} is the adversarial version of \system{DM}, pushing the encoder towards learning domain-independent source representations. These methods thus only use domain tags in training.
\item the multi-domain model of \cite{Zeng18multidomain} (\system{WDCMT}): in this approach, two representations, a domain-agnostic and a domain-specialized representation of the input are simultaneously processed; supervised classification models and adversarial training are used to compute these representations.\footnote{For this system, we use the available RNN-based system from the authors (\url{https://github.com/DeepLearnXMU/WDCNMT}\fyDone{URLs}) which does not directly compare to the other, Transformer-based, systems; the improved version of \cite{Su19exploring} seems to produce comparable, albeit slightly, improved results.}\fyTodo{Check this}
\item an original, multi-domain, version of the approach of \newcite{Bapna19simple}, denoted \system{MDL Res}, where a domain-specific adaptation module is included in all the Transformer layers; within each layer, residual connexions make it possible to by-pass this module.
  % In a variant (\system{MDL Gated}), we use a gating mechanism to merge computations using the the adapter modules and with those that don not.
Contrarily to \cite{Bapna19simple}, we do not start with a trained generic system, but learn the multi-domain from scratch.\fyDone{Check this.}
\end{itemize}

@@

\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}|} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c||}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
    \system{Mixed-Bal}   &  35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5 & 40.3  & 51.4 \\ %& \\
    \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.8 & 53.8\\
   \system{FT-Block}     & 37.3 & \SB{57.9} & 53.9 & 33.8 & \SB{46.7} & \SB{90.2}  & 42.3 & 53.3 \\ \hline % & 20.5\\ \hline
 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & \SB{80.5} &41.7 & 50.1    \\%    & 21.8 \\
    \system{DC-Feat}      & 37.7  & 54.9 & 49.5   & 32.9 & 43.6 & \SB{79.9} &41.4 & 49.9   \\% & \SW{21.7} \\
    \system{LDC-Tag}     & 37.0   & 54.7 & 49.9 & 33.9 & 43.6 & \SB{79.9} & & 49.8          \\% & 22.1 \\ 
    \system{TTM}            & 37.3 & 54.9 & 49.5 & 32.9 & 43.6 & \SB{79.9} &41.1 & 49.7     \\% &  23.4 \\
    \system{DM}             & \SW{35.6} & \SW{49.5}  & \SW{45.6}& \SW{29.9} & \SW{37.1} & \SW{62.4} & 39.7 & 43.8 \\ % & 22.6\\
    \system{ADM}           & 36.4 & \SW{53.5}  & \SW{48.3} & \SW{32.0} & \SW{41.5} & \SW{73.4} & 40.7 & 47.5 \\% & 23.3 \\
    \system{WDCMT}       & 34.6 & 51.7 & 47.5 & 29.4 & 36.5 & 49.3 & & 41.5 \\ % & 20.4 \\
    \system{MDL Res}     & 37.9 & \SB{56.0}  & \SB{51.2}   & 33.5   &  44.4  & \SB{88.3} & 42.1 & 51.9 \\%  & \SW{21.2} \\
    \hfill MDL Res (gen)    & 37.7 & 51.0 & 34.0 & 30.4 & 34.2 & 15.2 & 36.4 & 33.7\\
%    \system{MDL Gated} & 37.7 & 56.5 & 53.2 & 34.1 & 44.6 & 90.7 & 42.3 & 53.3&\\
     \hline
  \end{tabular}
  \caption{Translation performance of various MDMT systems. We report the BLEU score for each domain, as well as domain-weighted (w\domain{avg}) and unweighted (\domain{avg}) averages. Boldface denotes significant differences with respect to the \system{Mix-Nat} system.}
  \label{tab:performance}
  \fyTodo{Fill the table with all results, including a comparison with *RNNs* for wcmd}
  \fyTodo{Do we have significancy tests for averages?}
\end{table*}

@@

Table~\ref{tab:redomains} summaries the results of four experiments where we artificially redefine the boundaries of domains, with the aim to challenge requirements [P2-TUN], [P3-HET], and [P4-ERR]. In first three, we randomly \emph{split} one corpus in two parts and proceed as if this corresponded to two actual domains. A MD system should detect that these two pseudo-domains should be mutually beneficial, and should be hardly affected by this change with respect to the baseline scenario (no split). In this situation, we should expect MDMT to even surpass fine-tuning separately on each of these dummy domain, as MDMT exploits all data, where fine-tuning focuses only on a subpart. In testing, we decode the test set twice, once with each pseudo-domain tag. This makes no difference for \system{TMM}, \system{ADM}, \system{ADM} and \system{WDCMT}, which do not use domain tags in testing.
In the \textsl{merge} experiment, we do the reverse and merge two corpora in training, in order to assess the robustness with respect to heterogenous domains. We then translate the two corresponding test sets with the same (merged) system.

@@

We now turn to requirement [P5-UNK], and translate test sentences from a domain unseen in training (\domain{news}). For each test sentence, we automatically predict the most likely domain tag, and use it for decoding. Results are in the rightmost column of Table~\ref{tab:redomains}. In this configuration, all systems do worse than the \system{Mixed-Nat} baseline (Bleu=23.5), sometimes by a large margin.\fyTodo{Check significance, To be completed}

\subsubsection{Handling growing numbers of domains}
Another series of experiments evaluate the ability to dynamically handle suplementary domains (requirement [P6-DYN]) as follows. Starting with the existing MD systems of Section~\ref{ssec:rawperformance}, we introduce an extra domain (\domain{News}) and resume training with this new mixture of data\footnote{The design of a proper balance between domains in training is again of utmost importance for achieving optimal performance: since our goal is to evaluate all systems in the same conditions, we consider a basic mixing policy based on the new training distribution. This is of course detrimental to the small domains, for which the ``negative transfer'' effect is stronger than for larger domains.} for 50,000 additional iterations.\fyDone{Training regime of continuation} We contrast this approach with training all systems from scratch and report differences in performance in Table~\ref{tab:warmrestart}.
We expect that a proper MDMT system should not be significantly affected by the addition of a new domain, and reach about the same performance as if training with this domain from scratch. Note that from a practical viewpoint, dynamically integrating new domains is straightforward for \system{DC-Tag}, \system{DC-Feat} or \system{TTM} and the like, for which new domains merely add new labels. It is less simple for \system{LDC-Tag} and \system{MDL~Res}\fyDone{Complete effects of new domain}, for which the number of possible domains is built in the architecture and has to be anticipated from the beginning. This makes another difference between domain-bounded MT-systems, for which the number of domains is limited and truly open-domain systems.% , which seamlessly integrate additional domains.

\begin{table*}
  \begin{tabular}{|p{2.5cm}|*{9}{r|}} \hline \footnotesize
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{news}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline

    \system{Mixed-Nat}  & 37.3  & 54.6   & 50.1   & 33.5  & 43.2  & 77.5  & 23.5 & 41.1 & 49.4 \\
    \system{FT-Full}       & 37.7  & 59.2   & 54.5   & 34.0  & 46.8  & 90.8  & **** & 42.8 & 53.8 \\ \hline\hline

     \system{DC-Feat}     & 37.4 & 54.9   & 50.0    & 34.7  &  43.9  & 79.6 & 28.9  & & 50.1\\[-2pt]
%                   & 37.2 & 54.7   & 49.9    & 34.2  &  43.0  & 79.9 & \SW{28.1}  & &\\
                   & -0.2 & -0.1  & -0.1 & -0.6 & -0.9 & +0.3 & \SW{-0.8} & & -0.3\\

    \system{DC-Tag}      &  37.7 & 54.5   & 49.9    &  34.8 &  43.9  & 78.8 & 29.5  & & 49.9\\[-2pt]
%                                   & 38.0  & 54.4   & 49.2    & \SW{33.6}  &  \SW{42.7}  &\SW{75.3}  & \SW{28.1}  & & 48.9\\
                   & +0.3  & -0.1   & -0.6    & \SW{-1.1}  &  \SW{-1.3}  &\SW{-3.5}  & \SW{-1.4}  & & -1.2\\

    \system{LDC-Tag}    & 37.0   & 54.6  & 49.6    & 34.3  &  43.0  &77.0  & 28.7 & & 46.3 \\[-2pt]
                                   &&&&&&&& \\

    \system{TTM}           &  37.3 & 54.4   & 49.6    & 33.8  &  42.9  &78.2  & 29.1 & & 49.4\\[-2pt]
%                   & 37.1  & 54.2   & 49.1    & \SW{32.8}  &  42.0  &\SW{74.2}  & \SW{27.7}& 48.2\\
                    & -0.3  & -0.3  & -0.5    & \SW{-1.1}  &  -1.0  & \SW{-4.0}  & \SW{-1.4}& &-1.2\\

    \system{DM}            &36.0 &51.3&46.8&31.8&39.8&65.7&27.0 & & 45.2\\[-2pt]
%                   &36.5&51.7&47.4&31.7&40.3&65.7&\SW{25.8}& & \\
                   &+0.6&+0.4&+0.6&-0.1&0.5&0.0&\SW{-1.2}& & +0.3\\

    \system{ADM}          &36.6&54.2&49.1&32.9&42.1&75.7&28.7 & &4.4 \\[-2pt]
%                   &  36.9 &53.5&48.3&32.7&41.7&\SW{70.7}&\SW{26.8}& \\
                   & +0.3 & -0.8 & -0.8 & -0.2 & -0.4 & \SW{-5.0} & \SW{-1.9} & & -1.1\\

    \system{WDCMT}     &34.8  &51.8&47.8&30.7&37.3&49.3&25.9 & &\\[-2pt]
                    &&&&&&&& \\

    \system{MDL-Res}    &37.7   & 55.6   & 51.1   & 34.4  & 44.5  & 87.5  & 29.1 & & 51.8 \\[-2pt]
%                      & 37.5 & 56.1 & 51.1 & 34.0  &  44.3 & 87.3 & \SW{28.4} & & 51.7 & \\
                        & -0.2 & +0.5 & 0.0 & -0.4  &  -0.2 & -0.2 & \SW{-0.8} & & -0.1 \\
     \hline
  \end{tabular}
  \caption{Ability to handle new a domain: BLEU performance in ``resume training'' mode compared to a complete training session. Averages only take into account the six initial domains (\domain{News} excluded).}
  \label{tab:warmrestart}
  \fyTodo{Fill the table, significancy testing against initial learning condition, for each domain}
  \fyTodo{Need correct number / differences for Mixed-Nat}
  \fyDone{averages include one more domain ?}
\end{table*}

We can first compare the results of coldstart training with six (Table~\ref{tab:performance}) or seven domains (Table~\ref{tab:warmrestart}): the most striking observation is that the extra training data is detrimental for all systems and all domains,\fyTodo{is this significant ?}. Increasing the heterogeneity of the mix hurts performance across the board. This confirms that adding more out-of-domain data is not always helping, especially when domains are well separated. Comparing now the coldstart with the warmstart scenario, we see that the former is always significantly better for \domain{news}, as expected, and that resuming training can negatively impact the performance on other domains - this happens notably for \system{DC-Tag}, \system{TTM} and \system{ADM}. In this setting \system{MDL Res} and \system{DM} show the smaller average loss, with the former achieving the better balance of total training cost and average translation performance of all systems.

@@

\subsection{Automatic domains \label{ssec:autodomains}}
In this section, we experiment with automatic domains, obtained by clustering sentences into $k=30$ classes using the k-means algorithm based on generic sentence representations obtained via mean pooling as in section~\ref{ssec:corpora}. This allows us to evaluate requirement [P7-scale], training and testing our systems as if these domains were genuine. We also note that many of these classes are mere split of the large \domain{med}, while a few number of classes being mix of two existing domains. We are thus in a position to reiterate in more realistic conditions the measurements of section~\label{ssec:}, and to test whether multi-domain systems can effectively take advantage from the cross-domain similarities, and to eventually perform better that fine-tuning. Results are in table~\ref{tab:subdomains}.

\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}|} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c||}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
    \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.8 & 53.8\\
 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & \SB{80.5} &41.7 & 50.1    \\%    & 21.8 \\
    \system{DC-Feat}      & 37.7  & 54.9 & 49.5   & 32.9 & 43.6 & \SB{79.9} &41.4 & 49.9   \\% & \SW{21.7} \\
    \system{LDC-Tag}     & 37.0   & 54.7 & 49.9 & 33.9 & 43.6 & \SB{79.9} & & 49.8          \\% & 22.1 \\ 
    \system{TTM}            & 37.3 & 54.9 & 49.5 & 32.9 & 43.6 & \SB{79.9} &41.1 & 49.7     \\% &  23.4 \\
    \system{DM}             & \SW{35.6} & \SW{49.5}  & \SW{45.6}& \SW{29.9} & \SW{37.1} & \SW{62.4} & 39.7 & 43.8 \\ % & 22.6\\
    \system{ADM}           & 36.4 & \SW{53.5}  & \SW{48.3} & \SW{32.0} & \SW{41.5} & \SW{73.4} & 40.7 & 47.5 \\% & 23.3 \\
    \system{WDCMT}       & 34.6 & 51.7 & 47.5 & 29.4 & 36.5 & 49.3 & & 41.5 \\ % & 20.4 \\
    \system{MDL Res}     & 37.9 & \SB{56.0}  & \SB{51.2}   & 33.5   &  44.4  & \SB{88.3} & 42.1 & 51.9 \\%  & \SW{21.2} \\
     \hline
  \end{tabular}
  \caption{Translation performance with automatic domains, computed with the original test sets.}
  \label{tab:subdomains}
  \fyTodo{Fill the table with correct results,}
\end{table*}

@@

Multi-domain translation was already proposed for statistical MT, either considering as we do multiple sources of training data (eg.\ \cite{Banerjee10combining,Clark12onesystem,Sennrich13multidomain,Huck15mixeddomain}), or topically heterogeneous domains \cite{Eidelman12topic,Hasler14dynamic-topic}.\fyDone{Add also topic models refs} Two main strategies were considered: instance-based, involving a measure of similarities between train and test domains; feature-based, where domain/topic labels give rise to additional features.
